Distinction Centrality Analysis

### 2025-07-17 analysis.qmd
bom bom

```{r}
   d <- sapply(c, function(x) {x[2, 3]})
   dat <- data.frame(d = d, n = 1:length(d)) |> 
      mutate(n = n + 1)
   p <- ggplot(dat, aes(n, d, group = 1)) 
   p <- p + geom_point(size = 3, color = "blue")
   p <- p + geom_line(linewidth = 0.75, color = "blue")
   p <- p + geom_hline(yintercept = 0, color = "red", linetype = 2)
   p <- p + labs(y = "Gatekeeper Distinction", x = "Number of Branches")
   p <- p + scale_x_continuous(breaks = seq(2, length(d), by = 2))
   #p <- p + ylim(-0.1, 1)
   p <- p + theme_minimal()
   p <- p + theme(axis.text = element_text(size = 12),
                  axis.title = element_text(size = 14, face = "bold"))
   p <- p + ggtitle("Scalar Distinction of Star Node")
   p
   ggsave(here("Plots", "gatekeeper-by-nbranches.png"), width = 7, height = 7, units = "in")
```

```{r}
   d <- sapply(c, function(x) {x[nrow(x), 3]})
   dat <- data.frame(d = d, n = 1:length(d)) |> 
      mutate(n = n + 1)
   p <- ggplot(dat, aes(n, d, group = 1)) 
   p <- p + geom_point(size = 3, color = "blue")
   p <- p + geom_line(linewidth = 0.75, color = "blue")
   p <- p + geom_vline(xintercept = 3, color = "red", linetype = 2)
   p <- p + labs(y = "Gatekeeper Distinction", x = "Number of Branches")
   p <- p + scale_x_continuous(breaks = seq(2, length(d), by = 2))
   p <- p + theme_minimal()
   p <- p + theme(axis.text = element_text(size = 12),
                  axis.title = element_text(size = 14, face = "bold"))
   p
   ggsave(here("Plots", "pendant-by-nbranches.png"), width = 7, height = 7, units = "in")
```

>>>>

```{r}
   d <- sapply(c, function(x) {x[2, 3]})
   dat <- data.frame(d = d, n = 1:length(d)) |> 
      mutate(n = n + 1)
   p <- ggplot(dat, aes(n, d, group = 1)) 
   p <- p + geom_point(size = 3, color = "blue")
   p <- p + geom_line(linewidth = 0.75, color = "blue")
   p <- p + geom_hline(yintercept = 0, color = "red", linetype = 2)
   p <- p + labs(y = "Gatekeeper Distinction", x = "Number of Branches")
   p <- p + scale_x_continuous(breaks = seq(2, length(d), by = 2))
   #p <- p + ylim(-0.1, 1)
   p <- p + theme_minimal()
   p <- p + theme(axis.text = element_text(size = 12),
                  axis.title = element_text(size = 14, face = "bold"))
   p <- p + ggtitle("Scalar Distinction of Gatekeeper Node")
   p
   ggsave(here("Plots", "gatekeeper-by-nbranches.png"), width = 7, height = 7, units = "in")
```

```{r}
   d <- sapply(c, function(x) {x[nrow(x), 3]})
   dat <- data.frame(d = d, n = 1:length(d)) |> 
      mutate(n = n + 1)
   p <- ggplot(dat, aes(n, d, group = 1)) 
   p <- p + geom_point(size = 3, color = "blue")
   p <- p + geom_line(linewidth = 0.75, color = "blue")
   p <- p + geom_vline(xintercept = 3, color = "red", linetype = 2)
   p <- p + labs(y = "Gatekeeper Distinction", x = "Number of Branches")
   p <- p + scale_x_continuous(breaks = seq(2, length(d), by = 2))
   p <- p + theme_minimal()
   p <- p + theme(axis.text = element_text(size = 12),
                  axis.title = element_text(size = 14, face = "bold"))
   p <- p + ggtitle("Scalar Distinction of Peripheral Node")
   p
   ggsave(here("Plots", "pendant-by-nbranches.png"), width = 7, height = 7, units = "in")
```
